---
title: "Lab2"
output: pdf_document
date: "2023-04-16"
---

```{r load packages and set options, include=FALSE}
library(tidyverse) 
library(magrittr)
library(knitr)
library(patchwork)
library(moments)
library(car)
library(lmtest)
library(sandwich)
library(stargazer)
theme_set(theme_bw())
options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
```

## R Markdown

```{r}
grocery_data <- read.csv("data.csv")
```

```{r}
summary(grocery_data)
```

```{r}
update_weights <- function(data) {
  data %>%
    group_by(Item_Identifier) %>%
    mutate(Item_Weight = ifelse(is.na(Item_Weight), max(Item_Weight, na.rm = TRUE), Item_Weight)) %>%
    ungroup()
}

grocery_data <- update_weights(grocery_data)
grocery_data <- filter(grocery_data,Item_Visibility>0)
summary(grocery_data)
```

```{r}
dairy <- filter(grocery_data, Item_Type %in% c("Dairy"))
aggregate(dairy$Item_MRP, list(dairy$Outlet_Type), FUN=mean)
```

```{r}
fruits_and_veg <- filter(grocery_data, Item_Type %in% c("Fruits and Vegetables"))
aggregate(fruits_and_veg$Item_MRP, list(fruits_and_veg$Outlet_Type), FUN=mean)
```

```{r}
canned <- filter(grocery_data, Item_Type %in% c("Canned"))
aggregate(canned$Item_MRP, list(canned$Outlet_Type), FUN=mean)
```

```{r}
snacks <- filter(grocery_data, Item_Type %in% c("Snack Foods"))
aggregate(snacks$Item_MRP, list(snacks$Outlet_Type), FUN=mean)
```

```{r}
par(mfrow=c(2,2))
hist(grocery_data$Item_Visibility, xlab = 'Item Visbility', main = 'Histogram of Item Visibility')
hist(log(grocery_data$Item_Visibility), xlab = 'log(Item Visbility)', main = 'Histogram of Log Item Visibility')
hist(grocery_data$Item_Outlet_Sales, xlab = 'Outlet Sales', main = 'Histogram of Outlet Sales')
hist(log(grocery_data$Item_Outlet_Sales), xlab = 'log(Outlet Sales)', main = 'Histogram of Log Outlet Sales')
```

```{r}
hist(grocery_data$Item_MRP, xlab = 'Item MRP', main = 'Histogram of Item MRP')
hist(log(grocery_data$Item_MRP), xlab = 'log(Item MRP)', main = 'Histogram of Log Item MRP')
```

```{r}
# Split Data into Training and Testing in R 
sample_size = floor(0.7*nrow(grocery_data))
set.seed(777)

# randomly split data in r
picked = sample(seq_len(nrow(grocery_data)), size = sample_size)
train_data = grocery_data[-picked,]
test_data = grocery_data[picked,]

summary(train_data)
summary(test_data)
```

```{r}
# model_1 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility), data = train_data)
# model_2 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility) * Item_MRP, data = train_data)
# model_3 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility) * Item_MRP + Outlet_Type, data = train_data)

model_1 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility), data = test_data)
model_2 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility) * Item_MRP, data = test_data)
model_3 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility) * Item_MRP + Outlet_Type, data = test_data)
```

```{r}
# Perform an F test using anova()
anova(model_1, model_2, model_3)
```

```{r}
summary(model_1)
summary(model_2)
summary(model_3)
```

```{r}
dairy <- filter(test_data, Item_Type %in% c("Dairy"))
fruits_and_veg <- filter(test_data, Item_Type %in% c("Fruits and Vegetables"))
canned <- filter(test_data, Item_Type %in% c("Canned"))
snacks <- filter(test_data, Item_Type %in% c("Snack Foods"))
```

```{r}
model_4 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility) * Item_MRP + Outlet_Type, data = test_data)
model_5 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility) * Item_MRP + Outlet_Type, data = fruits_and_veg)
model_6 <- lm(log(Item_Outlet_Sales) ~ log(Item_Visibility) * Item_MRP + Outlet_Type, data = snacks)

summary(model_4)
summary(model_5)
summary(model_6)
```

```{r}
vif(model_2, type = 'predictor')
vif(model_3, type = 'predictor')
```

\newpage

```{r, results='asis'}
stargazer(model_1, model_2, model_3, column.sep.width = "3pt", font.size = "small", dep.var.labels = c('Log(Outlet Sales)'), title = 'Regression Model Results Comparing Models', covariate.labels = c('Log(Visibility)', 'Maximum Retail Price (MRP)', 'Type 1 Supermarket', 'Type 2 Supermarket', 'Type 3 Supermarket', 'Log(Visibility) - MRP Interaction', 'Constant'))
```

\newpage

```{r}
stargazer(model_4, model_5, model_6, column.sep.width = "3pt", font.size = "small", dep.var.labels = c('Log(Outlet Sales)'), title = 'Regression Model Results Comparing Item Data', covariate.labels = c('Log(Visibility)', 'Maximum Retail Price (MRP)', 'Type 1 Supermarket', 'Type 2 Supermarket', 'Type 3 Supermarket', 'Log(Visibility) - MRP Interaction', 'Constant'))
```

\newpage

```{r}
plot_one <- test_data %>%
ggplot(aes(x = resid(model_3))) + geom_histogram()
plot_two <- test_data %>%
ggplot(aes(sample = resid(model_3))) + stat_qq() + stat_qq_line()

plot_one / plot_two
```

```{r}
lmtest::bptest(model_4)
```

```{r}
ggplot(test_data, aes(predict(model_3), resid(model_3))) + geom_point() + stat_smooth()
```

```{r}
ggplot(test_data, aes(Item_Visibility, resid(model_3))) + geom_point() + stat_smooth()
ggplot(test_data, aes(Item_MRP, resid(model_3))) + geom_point() + stat_smooth()
ggplot(test_data, aes(Outlet_Type, resid(model_3))) + geom_point() + stat_smooth()
```

\begin{table}[!htbp] \centering 
  \caption{Regression Model Results Comparing Item Data} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{3pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{3}{c}{Log(Outlet Sales)} \\ 
\\[-1.8ex] & All Products & Fruits/Veg & Snack Foods \\ 
\hline \\[-1.8ex] 
 Log(Visibility) & 0.028$^{*}$ & 0.030 & 0.033 \\ 
  & (0.015) & (0.044) & (0.042) \\ 
  & & & \\ 
 Maximum Retail Price (MRP) & 0.008$^{***}$ & 0.008$^{***}$ & 0.008$^{***}$ \\ 
  & (0.0003) & (0.001) & (0.001) \\ 
  & & & \\ 
 Type 1 Supermarket & 1.954$^{***}$ & 1.966$^{***}$ & 2.003$^{***}$ \\ 
  & (0.014) & (0.038) & (0.040) \\ 
  & & & \\ 
 Type 2 Supermarket & 1.774$^{***}$ & 1.797$^{***}$ & 1.856$^{***}$ \\ 
  & (0.019) & (0.050) & (0.053) \\ 
  & & & \\ 
 Type 3 Supermarket & 2.476$^{***}$ & 2.593$^{***}$ & 2.526$^{***}$ \\ 
  & (0.019) & (0.050) & (0.053) \\ 
  & & & \\ 
 Log(Visibility) - MRP Interaction & $-$0.0002$^{**}$ & $-$0.0001 & $-$0.0001 \\ 
  & (0.0001) & (0.0003) & (0.0003) \\ 
  & & & \\ 
 Constant & 4.470$^{***}$ & 4.472$^{***}$ & 4.485$^{***}$ \\ 
  & (0.045) & (0.131) & (0.131) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 9,327 & 1,327 & 1,315 \\ 
R$^{2}$ & 0.789 & 0.796 & 0.768 \\ 
Adjusted R$^{2}$ & 0.789 & 0.795 & 0.767 \\ 
Residual Std. Error & 0.440 (df = 9320) & 0.442 (df = 1320) & 0.450 (df = 1308) \\ 
F Statistic & 5,807.752$^{***}$ (df = 6; 9320) & 857.568$^{***}$ (df = 6; 1320) & 720.034$^{***}$ (df = 6; 1308) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
